D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-19 ootavacuous.tex
Add examples and text for fungible stores
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

This appendix evaluates a number of OOTA-related litmus tests.
The evaluations are carried out using the \co{herd7} tool and also
using manual analysis.
The manual analysis uses the informal rule that a semantic dependency
exists between a given relaxed atomic load and store on any execution
where a different value loaded would change the address stored to, the
value stored, or the whether or not that store would be executed in
the first place.
Producing a precise formal statement of this rule turns out to be quite
challenging.

@@

% @@@ TODO:
% Convert remaining PPCMEM diagrams to herd7
% Emphasize that real-world implementations map abstract machine to matter
%	and energy in the real world.

>>>>

But beware of this example:

\begin{quote}
	\co{r1 = x;} \\
	\co{if (r1 > 0)} \\
	\co{\ \ \ \ y = 42;} \\
	\co{else} \\
	\co{\ \ \ \ y = 42;}
\end{quote}

Because the stores executed on each branch of that "if" statement
store identical values to identical addresses, they are for all intents
and purposes the same store.
Therefore, there is no semantic dependency~\cite{Howells2009membartxt}.

@@

This appendix evaluates a number of OOTA-related litmus tests.
The evaluations are carried out using the \co{herd7} tool and also
using manual analysis.
The manual analysis uses the informal rule that a semantic dependency
exists between a given relaxed atomic load and store on any execution
where a different value loaded would change the address stored to, the
value stored, or the whether or not that store would be executed in
the first place.
Producing a precise formal statement of this rule turns out to be quite
challenging.
For but one example, identical stores are fungible, so that if all
executions always execute one of several equivalently positioned stores
having identical addresses and values, there is no semantic dependency
from any load to any of those stores~\cite{Howells2009membartxt}.

@@

% @@@ TODO:
% Emphasize that real-world implementations map abstract machine to matter
%	and energy in the real world.
